Every Author as First Author

### 2023-03-29 paper.tex
BibTeX code

% Theme based on https://tex.stackexchange.com/a/283543/245104
\usepackage{xcolor}
\definecolor{commentgreen}{RGB}{2,112,10}
%\definecolor{eminence}{RGB}{108,48,130}
%\definecolor{eminence}{RGB}{81,36,97} % 25% darker
\definecolor{ours}{RGB}{0,71,171} % cobolt blue
\definecolor{frenchplum}{RGB}{129,20,83}
\usepackage{listings}
\lstset{
  language=[LaTeX]TeX,
  basicstyle=\ttfamily,
  numbers=left, numberstyle=\footnotesize,
  commentstyle=\slshape\color{commentgreen},
  alsoletter={@},
  moretexcs={pdftooltip,BeginAccSupp,EndAccSupp,@eol,patchcmd,texttransparent,NAT@nmfmt,NAT@citex,NAT@hyper@,@citea,hyper@natlinkbreak,NAT@nm,NAT@aysep,NAT@spacechar,@citeb,@extra@b@citeb,NAT@date,NAT@@open},
  keywordstyle=\color{frenchplum},
  emph={textstack,textstack@step,textstack@append,textstack@expand,namestack},
  emphstyle=\color{ours}
  %texcsstyle=*\color{frenchplum}
}

@@

\begin{abstract}
  We propose a new standard for writing author names on papers
  and in bibliographies, which places
  \emph{every author as a first author --- superimposed}.
  This approach enables authors to write papers as true equals,
  without any advantage given to whoever's name
  happens to come first alphabetically (for example).
  We develop the technology for implementing this standard
  in \LaTeX, \textsc{Bib}\TeX, and HTML;
  show several examples; and discuss further advantages.
\end{abstract}

@@

  \includegraphics[scale=0.5]{figs/tooltip-bib.png}
  \caption{Hovering over a name stack reveals the authors in their original
    order, as they would normally be written in the citation (above)
    or bibliography (below).  Screenshots from
    Visual Studio Code LaTeX Workshop Extension's internal PDF viewer,
    which is based on PDF.js.}
    % https://github.com/James-Yu/LaTeX-Workshop/wiki/View
  \label{fig:tooltip}
\end{figure}

@@

\subsection{\textsc{Bib}\TeX}

>>>>

% Theme based on https://tex.stackexchange.com/a/283543/245104
\usepackage{xcolor}
\definecolor{commentgreen}{RGB}{2,112,10}
%\definecolor{eminence}{RGB}{108,48,130}
%\definecolor{eminence}{RGB}{81,36,97} % 25% darker
\definecolor{ouridentifier}{RGB}{0,71,171} % cobolt blue
\definecolor{frenchplum}{RGB}{129,20,83}
\definecolor{stringorange}{RGB}{139,64,0} % dark orange
\definecolor{identifieryellow}{RGB}{82,81,0}
\usepackage{listings}
\lstset{
  language=[LaTeX]TeX,
  basicstyle=\ttfamily,
  numbers=left, numberstyle=\footnotesize,
  commentstyle=\slshape\color{commentgreen},
  alsoletter={@},
  moretexcs={pdftooltip,BeginAccSupp,EndAccSupp,@eol,patchcmd,texttransparent,NAT@nmfmt,NAT@citex,NAT@hyper@,@citea,hyper@natlinkbreak,NAT@nm,NAT@aysep,NAT@spacechar,@citeb,@extra@b@citeb,NAT@date,NAT@@open},
  keywordstyle=\color{frenchplum},
  emph={textstack,textstack@step,textstack@append,textstack@expand,namestack},
  emphstyle=\color{ouridentifier},
  stringstyle=\color{stringorange},
  identifierstyle=\color{identifieryellow},
  showstringspaces=false
  %texcsstyle=*\color{frenchplum}
}
\usepackage{multicol} % enables multicols=2

\def\BibTeX{\textsc{Bib}\TeX}

@@

\begin{abstract}
  We propose a new standard for writing author names on papers
  and in bibliographies, which places
  \emph{every author as a first author --- superimposed}.
  This approach enables authors to write papers as true equals,
  without any advantage given to whoever's name
  happens to come first alphabetically (for example).
  We develop the technology for implementing this standard
  in \LaTeX, \BibTeX, and HTML;
  show several examples; and discuss further advantages.
\end{abstract}

@@

  \includegraphics[scale=0.5]{figs/tooltip-bib.png}
  \caption{Hovering over a name stack reveals the authors in their original
    order, as they would normally be written in the citation (above)
    or bibliography (below).  Screenshots from
    VSCode's LaTeX Workshop Extension's internal PDF viewer
    \cite{latex-workshop-pdf}, which is based on PDF.js.}
  \label{fig:tooltip}
\end{figure}

@@

\subsection{\BibTeX}

% Minimal BibTeX mode
\lstset{
  alsoletter={$,.},
  keywords={FUNCTION, if$, while$, for$, swap$, num.names$, format.name$, int.to.str$, write$, newline$, cite$},
  string=[b]",
  % Emphasizing function names but not variables
  emph={namestack, format.names, format.full.names, make.full.names, calc.label, write.label, output.bibitem, before.all, output.state},
}

We modified the \texttt{abbrvnat.bst} bibliography style requested by this
proceedings to work with \lstinline|\namestack|;
refer to Listing~\ref{lst:bst} for the code.
First, we automatically wrap author/editor names within each bibliography entry
with \lstinline|\namestack{...}|.
We also append the number of names in a parenthetical;
this helps the reader know how many names are in each stack,
which we find particularly helpful in the context of this paper
for getting the feel for the newly introduced stacks.
Second, we output \texttt{natbib.sty}-compatible labels with semicolons
between all author names (instead of just the first author name followed by
``et al.''), so that the code in Listing~\ref{lst:natbib} constructs the
appropriate author stack.

\begin{lstlisting}[float=*,caption={Excerpts from \BibTeX\ style file, including all changed functions from \texttt{abbrvnat.bst}},label=lst:bst,multicols=2]
%% File: `stack-abbrvnat.bst'
%% A modification of `abbrv.bst' for use
%% with natbib package, further modified
%% for stacking names with \namestack

% Wrap top of stack in \namestack{...}
FUNCTION {namestack}
{ "\namestack{" swap$ * "}" *
}

% Format list of names (author or editor)
% on top of stack for inclusion in bibitem
FUNCTION {format.names}
{ 's :=
  #1 'nameptr :=
  s num.names$ 'numnames :=
  numnames 'namesleft :=
    { namesleft #0 > }
    { s nameptr "{f.~}{vv~}{ll}{, jj}"
      format.name$ 't :=
      nameptr #1 >
        { namesleft #1 >
            { "; " * t * }
            { t "others" =
                { " et~al." * }
                { "; " * t * }
              if$
            }
          if$
        }
        't
      if$
      nameptr #1 + 'nameptr :=
      namesleft #1 - 'namesleft :=
    }
  while$
  namestack
  % Append parenthetical number of names
  " (" * numnames int.to.str$ * ")" *
}

% Format list of names (author or editor)
% on top of stack for inclusion in
% natbib.sty label (just last names)
FUNCTION {format.full.names}
{'s :=
  #1 'nameptr :=
  s num.names$ 'numnames :=
  numnames 'namesleft :=
    { namesleft #0 > }
    { s nameptr
      "{vv }{ll}" format.name$ 't :=
      nameptr #1 >
        { "; " * t * }
        't
      if$
      nameptr #1 + 'nameptr :=
      namesleft #1 - 'namesleft :=
    }
  while$
}

% Omitted because not changed: make.full.names
% calls format.full.names with author or editor

% Compute label for sorting purposes (not used
% for actual output because it can overflow)
FUNCTION {calc.label}
{
  make.full.names
  "(" *
  year *
  ")" *
  'label :=
}

% Output natbib.sty label, without storing in
% a variable so won't overflow with many names
FUNCTION {write.label}
{
  make.full.names write$
  "(" write$
  year write$
  ")" write$
}

FUNCTION {output.bibitem}
{ newline$
  "\bibitem[" write$
  write.label
  "]{" write$
  cite$ write$
  "}" write$
  newline$
  ""
  before.all 'output.state :=
}
\end{lstlisting}
